\section*{Abbreviations}
\begin{longtable}{ll}
	\textbf{AI}       & Artificial Intelligence                   \\
	\textbf{BDI}      & Belief-Desire-Intention                   \\
	\textbf{CBT}      & Cognitive Behavioral Therapy              \\
	\textbf{CMA}      & Case Management Agent                     \\
	\textbf{DDDM}     & Data-Driven Decision-Making               \\
	\textbf{DSR}      & Design Science Research                   \\
	\textbf{FNR}      & False Negative Rate                       \\
	\textbf{HEI}      & Higher Education Institution              \\
	\textbf{HITL}     & Human-in-the-Loop                         \\
	\textbf{IA}       & Insights Agent                            \\
	\textbf{LCEL}     & LangChain Expression Language             \\
	\textbf{LLM}      & Large Language Model                      \\
	\textbf{LMS}      & Learning Management System                \\
	\textbf{MAS}      & Multi-Agent System                        \\
	\textbf{MoE}      & Mixture-of-Experts                        \\
	\textbf{ORM}      & Object-Relational Mapper                  \\
	\textbf{PET}      & Privacy-Enhancing Technology              \\
	\textbf{RBAC}     & Role-Based Access Control                 \\
	\textbf{RCT}      & Randomized Controlled Trial               \\
	\textbf{ReAct}    & Reasoning and Acting                      \\
	\textbf{RNN}      & Recurrent Neural Network                  \\
	\textbf{RQ}       & Research Question                         \\
	\textbf{STA}      & Safety Triage Agent                       \\
	\textbf{TCA}      & Therapeutic Coach Agent                   \\
	\textbf{UGM}      & Universitas Gadjah Mada                   \\
\end{longtable}

\section*{Nomenclature}
\begin{longtable}{llp{3.5in}}
	$A_t$               & \hspace{1cm} = & Therapeutic response from the TCA at time $t$.                           \\
	$a_t$               & \hspace{1cm} = & Action generated by a LangChain agent at step $t$.                       \\
	$Bel_t$             & \hspace{1cm} = & The set of an agent's beliefs at time $t$.                               \\
	$C_t$               & \hspace{1cm} = & The state of a clinical case for the CMA at time $t$.                    \\
	$\mathcal{C}$       & \hspace{1cm} = & The corpus of crisis patterns used by the STA.                           \\
	$d_k$               & \hspace{1cm} = & The dimension of the key vectors in a self-attention mechanism.          \\
	$Des_t$             & \hspace{1cm} = & The set of an agent's desires or goals at time $t$.                      \\
	$f_{\text{AGENT}}$  & \hspace{1cm} = & The core decision function of a specified agent (STA, TCA, CMA, IA).     \\
	$G$                 & \hspace{1cm} = & The initial goal or objective for a LangChain agent.                     \\
	$H_{t-1}$           & \hspace{1cm} = & The history of a conversation up to time $t-1$.                          \\
	$H_t$               & \hspace{1cm} = & The history of actions and observations for an agent up to step $t$.     \\
	$\mathcal{I}$       & \hspace{1cm} = & The library of evidence-based interventions available to the TCA.        \\
	$Int_t$             & \hspace{1cm} = & The set of an agent's intentions or committed plans at time $t$.         \\
	$K$                 & \hspace{1cm} = & The Key matrix in the self-attention mechanism.                          \\
	$\mathcal{K}$       & \hspace{1cm} = & The set of privacy constraints (e.g., k-anonymity) for the IA.           \\
	$k$                 & \hspace{1cm} = & The anonymity threshold in k-anonymity.                                  \\
	$M_t$               & \hspace{1cm} = & A message from a student at time $t$.                                    \\
	$\mathcal{M}$       & \hspace{1cm} = & A set of anonymized messages used by the IA.                             \\
	$\mu$               & \hspace{1cm} = & An aggregate metric computed by the IA.                                  \\
	$N$                 & \hspace{1cm} = & The set of nodes in a LangGraph state graph.                             \\
	$o_t$               & \hspace{1cm} = & An observation received by a LangChain agent at step $t$.                \\
	$p(\cdot)$          & \hspace{1cm} = & The conditional probability distribution of a Large Language Model.      \\
	$Q$                 & \hspace{1cm} = & The Query matrix in the self-attention mechanism.                        \\
	$q$                 & \hspace{1cm} = & An analytical query provided to the IA.                                  \\
	$R_t$               & \hspace{1cm} = & The risk level assessed by the STA at time $t$.                          \\
	$R_{\text{avail}}$  & \hspace{1cm} = & The set of available resources for the CMA.                              \\
	$\rho$              & \hspace{1cm} = & The routing function that determines the next node in a LangGraph.       \\
	$S_t$               & \hspace{1cm} = & The state of the LangGraph at time step $t$.                             \\
	$\Delta S_i$        & \hspace{1cm} = & The state update produced by node $i$ in a LangGraph.                    \\
	$th_t$              & \hspace{1cm} = & A thought or reasoning step generated by a LangChain agent at step $t$.  \\
	$V$                 & \hspace{1cm} = & The Value matrix in the self-attention mechanism.                        \\
	$W$                 & \hspace{1cm} = & Represents the various weight matrices within a Transformer model.       \\
\end{longtable}
